### 2024-02-14 documentation/thesis/thesis_document.tex
.

The sensor testing process involves two key tests. Firstly, the
linearity of the magnetic fields is measured with all sensors to assess
the feasibility of using specific sensors. Secondly, the homogeneity of
the sensors is evaluated to determine its capability to measure with
precision greater than 1,000 \gls{ppm}. In the end, the sensors should
also measure how uniform the magnetic field is in a completed \gls{mri}
system.

@@

The Halbach magnet incorporated in this system boasts a 27cm diameter, a
B0 field strength of 50.4 mT, and an impressive homogeneity of 2400 ppm
over a 20cm diameter using smaller magnets (\(12 x 12 x 12 mm^3\)). This
exceptional homogeneity enables the utilization of coil-based gradients
for spatial encoding, significantly enhancing the flexibility of image
acquisition.

@@

The focus of the ongoing efforts is to enhance the homogeneity of
magnets within low-field MRI systems below 1.000ppm, primarily driven by
the goal of establishing a compact low-field \gls{mri} for breast cancer
detection.

@@

This comprehensive effort serves to bolster the prototyping phase of the
low-field \gls{mri}. Diverging from the approach implemented by
O'Reilly, Teeuwisse, and Webb, DeLoRI aims to design an open \gls{mri},
departing from the circular \gls{mri} configuration discussed in the
publication. This innovation is geared towards streamlining breast
examinations, offering enhanced accessibility, and minimizing the
spatial requirements during installation. In addition DeLoRI endeavors
to achieve heightened accuracy, striving for precision levels below
1,000 ppm. While O'Reilly, Teeuwisse, and Webb were able to modify the
ring diameter to influence field homogeneity, the unique goal here is to
characterize the magnets pre-installation, allowing for proactive
assessments of homogeneity characteristics. This nuanced approach aims
to provide insights into magnetic field uniformity before the magnets
are integrated, thereby streamlining the optimization process.
Furthermore,

@@

Two sensors have been meticulously chosen for inclusion in the study.
The ultimate objective is to assess whether these selected sensors align
with the stringent criteria of achieving an accuracy level of 1,000 ppm.
Furthermore, the study seeks to validate whether the measuring range of
these sensors appropriately corresponds to the required field strength,
ensuring their suitability for the intended application.

@@

\begin{itemize}
\item
  Sensor Characterization: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than 1,000 ppm? The desired outcome is a
  measurement of less than 50 \(\mu\)T at 1,000 ppm, with a specific
  focus on determining the sensors' viability for noise measurements.
\end{itemize}

@@

This work successfully implemented a universal hardware and software
framework for the automated characterisation of permanent magnets. This
framework consists of a low-cost hardware interface that supports
various magnetic field sensors and a library for automating and
analysing the measurement data.

next step is the sensor evaluation

\begin{itemize}
\tightlist
\item
  software wurde erfolgreich evaluiert anhand der zuvor definierten
  usecases.
\item
  folgend wird der zweite anwendungsfall evaluiert mit der frage ob die
  magnete vermessen werden können
\item
  TODO
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  cheap sensors used
\item
  used hardware list
\item
  tested sensor tlv mmc, da diese zum zeitpunkt des tests zur verfüung
  standen
\end{itemize}

@@

\hypertarget{noise-level-data-analysis}{%
\subsection{Noise Level Data Analysis}\label{noise-level-data-analysis}}

@@

are they suitable for \textless1000ppm ?

@@

\hypertarget{recommendation-for-action}{%
\subsection{recommendation for action}\label{recommendation-for-action}}

>>>>

The sensor testing process involves two key tests. Firstly, the
linearity of the magnetic fields is measured with all sensors to assess
the feasibility of using specific sensors. Secondly, the homogeneity of
the sensors is evaluated to determine its capability to measure with
precision greater than 1000 \gls{ppm}. In the end, the sensors should
also measure how uniform the magnetic field is in a completed \gls{mri}
system.

@@

The Halbach magnet incorporated in this system boasts a 27cm diameter, a
B0 field strength of 50.4 mT, and an impressive homogeneity of 2400
\gls{ppm} over a 20cm diameter using smaller magnets
(\(12 x 12 x 12 mm^3\)). This exceptional homogeneity enables the
utilization of coil-based gradients for spatial encoding, significantly
enhancing the flexibility of image acquisition.

@@

The focus of the ongoing efforts is to enhance the homogeneity of
magnets within low-field MRI systems below 1000\gls{ppm}, primarily
driven by the goal of establishing a compact low-field \gls{mri} for
breast cancer detection.

@@

This comprehensive effort serves to bolster the prototyping phase of the
low-field \gls{mri}. Diverging from the approach implemented by
O'Reilly, Teeuwisse, and Webb, DeLoRI aims to design an open \gls{mri},
departing from the circular \gls{mri} configuration discussed in the
publication. This innovation is geared towards streamlining breast
examinations, offering enhanced accessibility, and minimizing the
spatial requirements during installation. In addition DeLoRI endeavors
to achieve heightened accuracy, striving for precision levels below 1000
\gls{ppm}. While O'Reilly, Teeuwisse, and Webb were able to modify the
ring diameter to influence field homogeneity, the unique goal here is to
characterize the magnets pre-installation, allowing for proactive
assessments of homogeneity characteristics. This nuanced approach aims
to provide insights into magnetic field uniformity before the magnets
are integrated, thereby streamlining the optimization process.
Furthermore,

@@

Two sensors have been meticulously chosen for inclusion in the study.
The ultimate objective is to assess whether these selected sensors align
with the stringent criteria of achieving an accuracy level of 1000
\gls{ppm}. Furthermore, the study seeks to validate whether the
measuring range of these sensors appropriately corresponds to the
required field strength, ensuring their suitability for the intended
application.

@@

\begin{itemize}
\item
  Sensor Characterization: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than 1,000 \gls{ppm}? The desired outcome is a
  measurement of less than 50 \(\mu\)T at 1000 \gls{ppm}, with a
  specific focus on determining the sensors' viability for noise
  measurements.
\end{itemize}

@@

In the previous chapter \emph{Usecase Evaluation}
\ref{usecase-evaluation} it was shown that the implementation of the
hardware and software framework for various magnetic field sensors was
successfully implemented.

In addition, the basic application by the user was demonstrated using an
example. This makes it possible to systematically characterise magnets
from the software and readout hardware side by means of data
acquisition, storage and analysis.

After discussing the developed hardware and software components in
particular, this chapter will answer the question of whether the
selected sensors meet the requirements:

\begin{itemize}
\tightlist
\item
  Measure a wide range of different permanent magnets with regard to
  their systematic field strength
\item
  Automated measurement of the homogeneity of Hallbach rings with an
  accuracy of less than 1000 \gls{ppm}
\end{itemize}

These questions are answered in the following, as a basic readout and
analysis functionality platform had to be created first and thus an
automated sensor characterisation can be performed.

\hypertarget{sensors-for-evaluation}{%
\section{Sensors for Evaluation}\label{sensors-for-evaluation}}

\begin{longtable}[]{@{}lll@{}}
\caption{Digital magnetic field sensors characterised for evaluation
\label{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}}\tabularnewline
\toprule
& TLV493D-A1B6 & MMC5603NJ\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D-A1B6 & MMC5603NJ\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D\tabularnewline
Temperature-Sensor & yes & yes\tabularnewline
Resolution {[}uT{]} & 98 & 0.007\tabularnewline
Range {[}mT{]} & ±130.0 & ±3\tabularnewline
Background-Noise {[}uT{]} & 100 & 0.2\tabularnewline
\bottomrule
\end{longtable}

@@

@@

@@

are they suitable for <1000(+\gls{ppm}) ?

@@

\hypertarget{recommendation-for-action}{%
\subsection{Recommendation for Action}\label{recommendation-for-action}}
